---
title: "Alcohol vs Seat choice"
author: "Dom Ciriello"
date: "Spring 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
  Our Goal is to answer this question: Is there a difference between the alcohol consumed between the row you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
  
This boxplot shows that the people who sit in the back row drink a lot more than the people who sit in the front or middle. The people who sit in the front consume the least and the people who sit in the middle consume the second least.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
  
The people who sit in the back drink considerably more than the people sitting in the other 2 rows. However, the people sitting in the middle drink slightly more than the people in the front.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
  
The people who sit in the back drink the most.

## Conclusions

In order of alcohol consumption from highest to lowest by seat row it would be: Back, Middle and then Front. So, yes, there is a difference in the amount of alcohol you consume and the row you choose to sit in.
